
---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 10 "
author: "Jingyu Wang"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 10 Exercises: 10.1, 10.2, 10.3, 10.4, 10.5, 10.6, 10.7  

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(dcData)
library(ggplot2)
```



## Chapter 10 Exercises

### Problem 10.1
1. str()
  + summary function
2. group_by()
  + data verbs
3. rank()
  + tranformation function
4. mean()
  + reduction function
5. filter()
  + data verbs
6. summary()
  + summary function
7. summarise()
  + data verbs
8. glimpse()
  + summary function

### Problem 10.2

1. Add a new column that is the ratio between two variables.
  + Using the mutate() data verb.
2. Sort the cases in descending order of a variable.
  + Using arrange() data verb.
3. Create a new data table that includes only those cases that meet a criterion.
  + Using the filter() data verb.
4. From a data table with three categorical variables A, B, & C, and a quantitative variable X, produce an output that has the same cases but only the variables A and X.
  + Using the select() to produce the output.
5. From a data table with three categorical variables A, B, & C, and a quantitative variable X, produce an output that has a separate case for each of the combinations of the levels of A and B. (Hints: This requires two different data verbs. It might be easier to see the answer if the problem statement added, “and gives the maximum value of X over all the cases that have a given combination of A and B.”)
  + Using the group_by() and summarise() data verbs to produce an output.

### Problem 10.3
1. Count the number of cases in a data table.
  + Using the nrow() to count the number of cases in a data table.
  
2. List the names of the variables in a data table.
  + Using the ls() function.
  
3. For data tables in an R package, display the documentation (“codebook”) for the data table.
Load a package into your R session.
  + We using the library("codebook") function to laod a package into the R session.

4. Mark a data table as grouped by one or more categorical variables.
  + We using group_by() to mark a data table as grouped by one or more categorical variables.
  
### Problem 10.4
1. Output Table A
```{r}
data("BabyNames", package = 'dcData')
BabyNames %>% 
  arrange(count)
```


2. Output Table B
```{r}
BabyNames %>% 
  filter(sex == "F")
```

3. Output Table C
```{r}
BabyNames %>% 
  filter(sex == "M")
```

4. Output Table D
```{r}
Minneapolis2013 %>%
  summarise( total = n() )
```

5. Output Table E
```{r}
BabyNames %>%
  group_by( name,count ) %>% 
  arrange(count)
```

### Problem 10.5
1. How many people chose the same candidate for both First and Second place?
```{r}
data("Minneapolis", package = 'dcData')
Minneapolis2013 %>%
  filter(First == Second, First != Third) %>%
  summarise(total= n())
```
  + I try to found the First and Second contain the same result, so I use the filter and summarise function to see how many of them are same. There are 304 chose the same candidate for bothe first and second place.


2. Of the ballots where the First and Second place choices are the same, what were the top 3 choices?
```{r}
Minneapolis2013 %>%
  group_by(First, Second) %>%
  filter(First == Second, First != Third) %>%
  summarise(total= n()) %>%
  arrange(desc(total)) %>%
  head(10)
```
  + We ask to fund the top 3 thir choice are the same, so I choose group_by and filter function to set the condition. Also using the arrange to see which of them are the top 3. The top 3 are Betsy Hodges, Mark andrew, and Don Samuels.

3. Of the people who selected Ole Savior for First, what were the top three Second choices?
```{r}
Minneapolis2013 %>%
  filter(First == "OLE SAVIOR") %>%
  group_by(First, Second) %>%
  summarise(total = n()) %>%
  arrange(desc(total)) %>%
  head(10)
```
  + We are ask to find people select Ole Savior first, then what were the top three second choices. So I set First equal to Ole Savior, then using the arrange descending function to see who are the top 3. The top 3 are Cam Winton, Christopher Robin Zimmerman, and Ole Savior.
  
### Problem 10.6
1. Which color diamonds seem to be largest on average (in terms of carats)?
```{r}
data("diamonds", package = "dcData")
diamonds %>% 
  group_by(color) %>%
  mutate(mean = sum(mean(table/carat))) %>% 
  arrange(desc(mean)) %>%
  head( 1 )
```
  + The color E seem to be largest on average.

2. Which clarity of diamonds has the largest average “table” per carat?
```{r}
diamonds %>% 
  group_by(clarity) %>%
  mutate(mean = sum(mean(table/carat))) %>% 
  arrange(desc(mean)) %>%
  head( 1 )
```
  + The clarity VVS1 seems to has the largest average per carat.

### Problem 10.7
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(total = n()) %>%
  mutate(minor = (total < 5000)) %>%
  arrange(desc(total))
```

