---
title: "Activity: Popular Names"
author: "Jingyu Wang"
date: "03.01.2020"
output: html_notebook
---



# Set Up

```{r}
# clean up
rm(list = ls())

# packages in use
library(tidyverse)
library(dcData)
library(esquisse)
```


```{r}
# data intake 
data("BabyNames", package = "dcData")

```

# Activity

**Goal**: By the end of the activity, each team will create a graph similar to the Figure in the book showing ups and downs in the popularity of four names (your own & at least three additional names) according to the U.S. social security administration provided in the `dcData` pacakge 


### Step 1
```{r}
view(data)
help("BabyNames")
```


By viewing the dataset, I found "BabyNames" dataset contains four variables, which are name, sex, count, and year. Also this dataset contains 1792091 cases, which are very large number, because this is a raw data. 

### Step 3
1. What variable(s) from the raw data table do not appear at all in the graph?
  + I found that count variable does not appear at all in the graph.

2. What variable(s) in the graph are similar to corresponding variables in the raw data table, but might have been transformed in some way?
  + From my perspective, the popularity variable in the graph are similar to count variable in the raw data, popularity is a transformation and calculartion from count.


### Step 4
1. Have cases been filtered out?
  + Yes the cases have been filtered out.
  
2. Have cases been grouped and summarized within groups in any way?
  + Yes the cases been grouped and summarized within groups, I grouped name and year, then summarized by the total. I also 

3. Have any new variables been introduced? If so, what’s the relationship between the new variables and existing variables?
  + I create a new variable called pop, which means the "popularity" of the name, I took log10 of the count to create this new variable.


### Step 5

First I discovering the whole dataset, I found there has four columns in the dataset.Then I group the data and summarise by sex and name to see the total number of the name. Then I use filter function to see the most popular girl names after 1996. After that I use head function to see the top 10 name of the dataset. The I use mutate function to create a new variable called pop, which means the popularity, it is log10 of the variable count. Then I try some steps with the pop variable. First I try the name "Emily" to see this name's popularity acrossing each years, the I use filter and arrange function to see the popularity of girl's names and boy's names.

### Step 7

```{r}
Result <- 
  BabyNames %>% 
  group_by( name, year ) %>%
  summarise( total = sum( count ) )
Result
```


```{r}
BabyNames %>% 
  filter(year > 1995, sex == "F")
```

```{r}
head(BabyNames, n = 10)
```

```{r}
BabyNames <-
  BabyNames %>% 
  mutate(popularity = log10(count))
```

```{r}
BabyNames %>%
  filter(name == "Emily" & sex == "F") %>%
  arrange(desc(popularity))
```

```{r}
BabyNames %>%
  filter(sex == "F") %>%
  arrange(desc(popularity))
```

```{r}
BabyNames %>%
  filter(sex == "M") %>%
  arrange(desc(popularity))
```

```{r}
BabyNames %>%
  filter(sex=="F") %>%
  filter(name %in% c("Emily","Erica","Anna","Jingyu")) %>% 
  ggplot(., aes(year, popularity)) +
  geom_line(aes(color=name), lwd=1) +
  theme_bw()

```
